An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-15 poly-embed-journal/poly-embed-journal.tex
Pre-meeting notes

\item \raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
  Hence, there is some unique $\H' \subseteq \H$ such that $G = \cap \H'$. \jessie{$\H \subseteq \H$ since $G = \cap \H' = \cap \H$; something about smallest cardinality here?}
  Moreover, each $H\in\H'$ defines a facet \raf{make formal}
  \begin{proof}
	\jessie{Incomplete}
	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
  \end{proof}
\item 
\begin{claim}
	$\H_\Y \subseteq \H'$.
\end{claim}
\begin{proof}
	We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
	The first cannot happen as we take $f$ to be defined (and finite) on $p = \delta_y \in \simplex$, and $f$ and $g$ match on the domain of $f$.
	Moreover, the second cannot be true by construction of $g$.	
\end{proof}
\item 
\begin{corollary}
	Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$; That's the $\V$ we are looking for.  (And we've argued that it's uniquely determined by $f$.) \jessie{Why is $\V$ minimum cardinality?}
\end{corollary}
\item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.
\item Claim: $F_v$ is a facet of $G$ for each $v\in\V$.  \raf{Unpacking ``defines a facet''}
\end{itemize}

>>>>

\item \raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
  Hence, there is some unique $\H' \subseteq \H$ such that $G = \cap \H'$. \jessie{$\H \subseteq \H$ since $G = \cap \H' = \cap \H$; something about smallest cardinality here?}
  Moreover, each $H\in\H'$ defines a facet \raf{make formal}
  \begin{proof}
	\jessie{Incomplete}
	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
  \end{proof}
\item 
\begin{claim}
	$\H_\Y \subseteq \H'$.
\end{claim}
\begin{proof}
	We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
	The first cannot happen as we take $f$ to be defined (and finite) on $p = \delta_y \in \simplex$, and $f$ and $g$ match on the domain of $f$.
	Moreover, the second cannot be true by construction of $g$.	
\end{proof}
\item 
\begin{corollary}
	Then $\H' \setminus \H_\Y = \{H_v^+ : v\in\V\} =: \H_\V$ for some $\V \subseteq \hat \V$; That's the $\V$ we are looking for.  (And we've argued that it's uniquely determined by $f$.) \jessie{Why is $\V$ minimum cardinality?}
\end{corollary}
\item Define $F_v := H^+_v \cap G$ for any $v\in\reals^\Y_+$.
\item Claim: $F_v$ is a facet of $G$ for each $v\in\V$.  \raf{Unpacking ``defines a facet''}
\begin{proof}
	First, observe that by construction, $H_v = \{(x,c) \mid \inprod{v}{x} - c \geq 0\}$ is a valid inequality for $G$, and thus $F_v$ is a face of $G$ by definition.
	To see that $F_v$ is a facet, we must show it is $\dim(G) - 1 = |\Y|$-dimensional.
	This holds true if we can fit a $|\Y|$-dimensional ball in $F_v$.
	If we could not fit such a ball in $F_v$, \jessie{contradict $\V$ minimum cardinality}
\end{proof}
\end{itemize}
